---
title: "Classification"
author: ""
date: ""
output: 
  html_document:
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

## Packages and Data

```{r packages-data}
library(tidyverse)
library(class)
pokemon <- read_csv("data/pokemon_cleaned.csv", na = c("n/a", "", "NA"))
```

## Exercises

1. Train the k-NN model using all existing Pokemon and create a logistic 
   regression model for legendary status. For the following hypothetical 
   Pokemon, classify them as being legendary vs. non-legendary using both k-NN 
   and logistic regression. When using k-NN, try varying the chosen $k$ and 
   compare/contrast the results. 

    - HP: 91,  ATK: 134, DEF: 95,  SPA: 100, SPD: 100, SPE: 80
    - HP: 30,  ATK: 60,  DEF: 180, SPA: 50,  SPD: 180, SPE: 50
    - HP: 105, ATK: 95,  DEF: 60,  SPA: 95,  SPD: 60,  SPE: 90
    - HP: 45,  ATK: 55,  DEF: 60,  SPA: 60,  SPD: 50,  SPE: 35
    - HP: 100, ATK: 130, DEF: 110, SPA: 90,  SPD: 80,  SPE: 100

<br/>

2. When using logistic regression, which has the highest estimated probability 
   of being a legendary Pokemon?

## Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.
